---
params: 
    set_title: "Religion"
title: "`r params$set_title`"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: united
---

```{r setup, include=FALSE}
setwd('C:\\Users\\310228580\\Google Drive\\Analytics\\Datasets\\Religious Texts')

library(flexdashboard)
library(dplyr)
library(streamgraph)
library(reshape2)
library(ggplot2)
library(highcharter)
library(RColorBrewer)
library(stringr)
library(visNetwork)

all_data = read.csv2('output\\emotion_count.csv', sep = ",", stringsAsFactors = FALSE)


num_data <- data.frame(data.matrix(all_data))
numeric_columns <- sapply(num_data,function(x){mean(as.numeric(is.na(x)))<0.5})
all_data <- data.frame(cbind(num_data[,numeric_columns], all_data[,!numeric_columns]))
all_data %>% rename(File=file)->all_data

names(all_data) <-str_to_title(names(all_data))

all_data %>% 
  select(-c(Chapter,Chapter_names)) %>% 
  group_by(File) %>% 
  summarise_all(sum)-> total_summary

norm_summary = cbind(total_summary)

# norm_summary[,(2:11)] %>%  sapply(`/`, norm_summary[,12]) -> norm_summary[,(2:11)] 
norm_summary[,(2:11)] %>%  sapply(`/`, rowSums(norm_summary[,(2:11)])) %>% sapply(`*`, 100)  -> norm_summary[,(2:11)] 

norm_summary%>%
  select(-c(Positive, Negative, Word_counts)) %>% 
  melt() -> radar_dat 

color_list=brewer.pal(6,"Spectral")

radar_list = c('King James Bible','Koran','Gita','Gospel of Buddha','Mahabharata', 'Meditations')

plot_radar <- function(radar, color){
  hchart(radar_dat %>% filter(File==radar), 
       'area',hcaes(x = variable, y = value), 
       fillOpacity=1, marker = list(enabled = FALSE),
       color=color) %>% 
  hc_chart(polar = TRUE) %>% 
  hc_xAxis(tickmarkPlacement = "on",
           lineWidth = 0,
           title = list(
             text = NULL
           )) %>% 
  hc_yAxis(gridLineInterpolation = "polygon",
           lineWidth = 0,
           min = 0,
           title = list(text = NULL),
           labels = list(enabled=FALSE)) %>% 
  hc_tooltip(valueDecimals = 3,
             pointFormat = "{point.y:.2f} %") %>% 
      hc_plotOptions(series=list(lineColor = '#303030',lineWidth =1))-> hc
  return (hc)
}
```
Emotions in Religious Texts {data-orientation=rows}
=====================================  
Row
-------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[1]`<span>

```{r}

i=1
radar = radar_list[i]
color = color_list[i]

plot_radar(radar, color)


```

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[2]`<span>

```{r}

i=2
radar = radar_list[i]
color = color_list[i]
plot_radar(radar, color)

```

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[3]`<span>

```{r}


i=3
radar = radar_list[i]
color = color_list[i]
plot_radar(radar, color)
```

Row
-------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[4]`<span>

```{r}

i=4
radar = radar_list[i]
color = color_list[i]
plot_radar(radar, color)

```

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[5]`<span>

```{r}


i=5
radar = radar_list[i]
color = color_list[i]
plot_radar(radar, color)
```

### <span style="font-weight:thin; font-size: 1.5em;">`r radar_list[6]`<span>

```{r}
i=6
radar = radar_list[i]
color = color_list[i]
plot_radar(radar, color)
```

King James Bible
=====================================  

```{r setup_bible, include=FALSE}
BOOK = 'King James Bible'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph Bible}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado Bible}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart Bible}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

Koran
=====================================  

```{r setup_koran, include=FALSE}
BOOK = 'Koran'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph Koran}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado Koran}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart Koran}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

Gita
=====================================  

```{r setup_gita, include=FALSE}
BOOK = 'Gita'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph Gita}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado Gita}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart Gita}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

Gospel of Buddha
=====================================  

```{r setup_buddha, include=FALSE}
BOOK = 'Gospel of Buddha'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph Buddha}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado Buddha}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart mahaharata}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

Mahabharata
=====================================  

```{r setup_mahabharata, include=FALSE}
BOOK = 'Mahabharata'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph mahabharata}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado mahabharata}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart mahabharata}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

Meditations
=====================================  

```{r setup_meditations, include=FALSE}
BOOK = 'Meditations'

all_data[all_data$File == BOOK,] %>% select(-c(Chapter_names)) -> data_book
```
Column {data-width=650}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Emotions across the Chapters<span>
&emsp;<span style="background-color:#D53e4f;">&emsp;</span> Anger &emsp; 
<span style="background-color:#f46d43;">&emsp;</span> Anticipation &emsp; 
<span style="background-color:#fdae61;">&emsp;</span> Disgust &emsp; 
<span style="background-color:#fee08b;">&emsp;</span> Fear &emsp;
<span style="background-color:#e6f598 ;">&emsp;</span> Joy &emsp;
<span style="background-color:#abdda4 ;">&emsp;</span> Sadness &emsp;
<span style="background-color:#66c2a5 ;">&emsp;</span> Surprise &emsp;
<span style="background-color:#3288bd ;">&emsp;</span> Trust &emsp;

```{r Emotion Streamgraph meditation}
#### Stream Graph Emotions
data <- select(data_book, -c(Word_counts,Positive,Negative,File))
l<-length(data$Chapter)
data <-melt(data, id = c("Chapter"))
data$X = seq(as.Date("2012/1/1"), by = "day", length.out = l)
# data$variable = lapply(data$variable, str_to_title)
# Basic stream graph: just give the 3 arguments
streamgraph(data, key="variable", value="value", date="X", interpolate="cardinal") %>% 
  sg_axis_x(1,'chapter',"%-j") %>% 
  sg_axis_y(tick_count = 0)

```

Column {data-width=350}
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1.5em;">Sentiments across the Chapters<span>

```{r Sentiment Tornado meditation}
# #### Tornado Sentiment

all_data %>% 
  filter(File == BOOK) %>% 
  select(Chapter, Chapter_names, Positive, Negative, Word_counts) %>% 
  mutate(Total = Positive + Negative,Negative = -(Negative)) -> tor_chapter_dat

norm_chapter_tor = cbind(tor_chapter_dat)

norm_chapter_tor[,(3:4)] %>%  sapply(`/`, norm_chapter_tor[,5]) -> norm_chapter_tor[,(3:4)]

norm_chapter_tor %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% 
  left_join(tor_chapter_dat %>%select(-c(Word_counts,Total)) %>%  melt(id=c('Chapter','Chapter_names')) %>% rename(value_count=value)
            , by=c('Chapter','Chapter_names','variable'))->tor_df


hchart(tor_df, type='bar', hcaes(x='Chapter_names', y='value', group='variable')) %>% 
  hc_tooltip(pointFormat = "Here is the doctor {point.value_count}") %>% 
  hc_plotOptions(
    series = list(stacking = "normal"),
    bar = list(groupPadding = 0.1, pointPadding =  0, borderWidth = 0)
  ) %>% 
  hc_xAxis(categories = norm_chapter_tor$Chapter_names) %>% 
  hc_yAxis(visible=FALSE) %>% 
  hc_tooltip(pointFormat = "{series.name} : {point.value_count} <br>", shared=TRUE) %>% 
  hc_colors(c('#66c2a5','#d53e4f'))

```

### <span style="font-weight:thin; font-size: 1.5em;">Emotions in the book<span>

```{r Donut Chart meditations}

data_book %>% 
  select(-c(Positive,Negative,Word_counts,File)) %>%
  melt(id='Chapter') %>%
  select(-c(Chapter)) %>%
  mutate(value = as.numeric(value)) %>% 
  group_by(variable) %>% 
  summarise(count=sum(value)) %>% 
  rename(category = variable)->dat

dat$category %>% unique() %>% sort() -> category

dat %>% 
left_join(cbind.data.frame(category,color=brewer.pal(8,"Spectral")), by = 'category') -> dat


hchart(dat, 'pie',hcaes(name = category, y = count, color=color), size = '100%', innerSize = "60%", showInLegend = FALSE) %>% 
  hc_colors(brewer.pal(8,"Spectral")) %>% 
  hc_tooltip(valueDecimals = 0,
             pointFormat = "Word Count: {point.y}")
```

```{r setup_word_assoc, include=FALSE}
node_df <- read.csv2('node.csv', sep = ",", stringsAsFactors = FALSE)
link_df <- read.csv2('link.csv', sep = ",", stringsAsFactors = FALSE)

book_list <- unique(node_df$book)

draw_network<- function(x){
  node_seed %>% 
    filter(book==x)->nodes
  link_seed %>% 
    filter(book==x)->links
  if (length(nodes$id)>0){
      nodes$shape <- "dot"  
      nodes$shadow <- FALSE # Nodes will drop shadow
      nodes$title <- nodes$word # Text on click
      nodes$label <- nodes$word # Node label
      # nodes$size <- nodes$word_count# Node size
      nodes$size <- lapply(nodes$level, function(x){return (ifelse(x==0, 50,((1/x)*25)))})# Node size
      nodes$borderWidth <- 2 # Node border width
      nodes$font.size = 25
      
      # nodes$color.background <- brewer.pal(8,"Spectral")[c(1,7,8)][nodes$level+1]
      nodes$color.background <-rep(brewer.pal(8,"Spectral"),length.out=length(nodes$id))
      nodes$color.border <- "black"
      nodes$color.highlight.background <- "orange"
      nodes$color.highlight.border <- "darkred"
      
      links$length <- links$similarity
      
    }
  
  return (visNetwork(nodes, links))
}

```

Love {data-navmenu="Word Associations" data-icon="fa-heart" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'love'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

God {data-navmenu="Word Associations" data-icon="fa-google" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'god'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Faith {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'faith'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Evil {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'evil'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Money {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'money'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Heaven {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'heaven'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Hell {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'hell'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Hate {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'hate'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```

Jihad {data-navmenu="Word Associations" data-icon="fa-facebook-f" data-orientation=rows} 
=====================================  

```{r, include=FALSE}

seed_word = 'jihad'
node_df %>% 
  filter(seed == seed_word) -> node_seed

link_df %>% 
  filter(seed == seed_word) -> link_seed

lapply(book_list,function(x) draw_network(x)) -> network_list

```
Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Gospel of Buddha<span>

```{r}
network_list[[1]]
```

### <span style="font-weight:thin; font-size: 1em;">Gita<span>

```{r}
network_list[[2]]
```

### <span style="font-weight:thin; font-size: 1em;">King James Bible<span>

```{r}
network_list[[3]]
```

Row
-----------------------------------------------------------------------

### <span style="font-weight:thin; font-size: 1em;">Quran<span>

```{r}
network_list[[4]]
```

### <span style="font-weight:thin; font-size: 1em;">Mahabharata<span>

```{r}
network_list[[5]]
```

### <span style="font-weight:thin; font-size: 1em;">Meditation<span>

```{r}
network_list[[6]]
```
